---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)

```

```{css}
body {
  background-color: #f9f9f9;
  font-family: Arial, sans-serif;
  font-size: 18px;
}

h1 {
  color: #336699;
  font-size: 36px;
}

h2 {
  color: #824670;
  font-size: 28px;
  margin-top:30px;
}

img {
  display: block;
  margin-left: auto;
  margin-right: auto;
  border: 3px solid #d9cfc1;
  border-radius: 10px;
  padding: 5px;
}
```

## Headphone usage in public spaces

This report presents observational data on headphone usage in different public spaces. The data was collected across multiple observations, recording the number of people wearing headphones, the total number of people in the observation area, the most commonly observed headphone type, the location, and the time of day.

```{r}
# Load tidyverse package
library(tidyverse)

# Import survey data
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQLUgGUihmvvz_DutjxNjnmKPwgq92AzYAbTYkkDlYWTHmuQ2zKTEyYGCrJPnSK21wjsmFpjeGQMZ5d/pub?gid=530894597&single=true&output=csv")

# Rename the variables of the data frame
latest_data <- logged_data %>%
  rename(
    headphone_count = `How many people are wearing headphones in your observation area?`,
    total_people = `Approximately how many people are in the observation area?`,
    headphone_type = `What type of headphone is most commonly observed?`,
    location = `Where is this observation taking place?`,
    time_of_day = `What time of day is this observation?`
  )

# Create new variable for proportion
latest_data <- latest_data %>%
  mutate(
    headphone_prop = headphone_count / total_people
  )

#summary_stats
summary_stats <- latest_data %>%
  summarise(
    mean_headphones = mean(headphone_count, na.rm = TRUE),
    max_headphones = max(headphone_count, na.rm = TRUE),
    mean_headphone_prop = mean(headphone_prop, na.rm = TRUE)
  )

mean_headphones <- summary_stats$mean_headphones
max_headphones <- summary_stats$max_headphones
mean_prop <- summary_stats$mean_headphone_prop

# number of observations
n_observations <- nrow(latest_data)

# Count for headphones type and locations
type_counts <- count(latest_data, headphone_type)

location_counts <- count(latest_data, location)

# Most common headphone type and locations
most_common_type <- type_counts %>%
  arrange(desc(n)) %>% slice(1)

most_common_location <- location_counts %>%
  arrange(desc(n)) %>% slice(1)

```

A total of `r n_observations` observations were recorded.

On average, about `r round(mean_headphones, 1)` people were wearing headphones in each observation.

The highest number of people wearing headphones in a single observation was `r max_headphones`.

On average, around `r round(mean_prop * 100, 1)`% of people in an observation area were wearing headphones.

The most commonly observed headphone type was `r most_common_type$headphone_type`, with `r most_common_type$n` observations.

The location with the most observations was `r most_common_location$location`.

```{r}
# Bar chart 1: Headphone type 

ggplot(latest_data, aes(x = stringr::str_wrap(headphone_type, width = 15))) +
  geom_bar() +
  labs(
    title = "Most commonly observed headphone type",
    x = "Headphone type",
    y = "Number of observations"
  ) +
  theme(plot.title = element_text(hjust = 0.5))
```

```{r}
# Bar chart 2: Headphone type by location 

ggplot(latest_data, aes(x = stringr::str_wrap(location, width = 15), fill = headphone_type)) +
  geom_bar() +
  labs(
    title = "Headphone type observed by location",
    x = "Location",
    y = "Number of observations",
    fill = "Headphone type"
  ) +
  theme(plot.title = element_text(hjust = 0.5))
```

The bar charts show that in-ear headphones are the most commonly observed type. The distribution of headphone types also varies across different locations.
